Deep Reinforcement Learning for Conservation Decisions

### 2022-05-27 manuscript/manuscript.Rmd
Some edits, more to come

Despite relevance to decision making under uncertainty that could make RL uniquely well suited for ecological conservation, RL has not been widely applied across this field.
To date, the problems considered by RL research have largely been drawn from examples in robotic movement and games like Go and Starcraft [@openai_learning_2019; @alphazero; @alphastar].
Complex environmental problems share many similarities to these tasks and games: the need to plan many moves ahead given a large number of possible outcomes, to account for uncertainty and to respond with contingency to the unexpected.
RL agents typically develop strategies by interacting with simulators, a practice that should not be unsettling to ecologists since learning from simulators is common across ecology.
Rich, processes-based simulations such as the SORTIE model in forest management [@sortie], Ecopath with Ecosim in fisheries management [@ecopath], or climate change policy models [@dice] are already used to explore scenarios and inform ecosystem management.
Decision-theoretic approaches based on optimal control techniques can only find the best strategy in the simplest of ecological models; the so called "curse of dimensionality" makes problems with a large number of states or actions intractable by conventional methods [@Possingham2006; @Marescot2013; @ferrer-mestres_k-n-momdps_2021; @chades_primer_2021].
Neural-network-based RL techniques, referred to as *deep RL*, have proven particularly effective in problems involving complex, high-dimensional spaces that have previously proven intractable to classical methods.

@@

Neural networks become useful in RL when the environment has a large observation-action space^[Conventionally, an observation-action space is considered to be large when it is non-tabular, i.e. cannot be represented in a computationally tractable table.], which happens frequently with realistic decision-making problems. 
Whenever there is a need for an agent to approximate some function, say a policy function, neural networks can be used in this capacity due to their property of being general function approximators [@universalapproximators].
Although there are other function approximators that can be used in RL, e.g. Gaussian processes [@grande14], neural networks have excelled in this role because of their ability to learn complex, non-linear, high dimensional functions and their ability to adapt given new information [@briefsurveydrl].
There is a multitude of deep RL algorithms since there are many design choices that can be made in constructing a deep RL agent -- see Appendix A for more detail on these engineering decisions. 
In Table 1, we present some of the more common deep RL algorithms which serve as good reference points for the current state of deep RL.

>>>>

Despite relevance to decision making under uncertainty that could make RL uniquely well suited for ecological conservation, RL has only been applied to this field in a few cases [@xu_robust_2021, @silvestro_improving_2022].
To date, the problems considered by RL research have largely been drawn from examples in robotic movement and games like Go and Starcraft [@openai_learning_2019; @alphazero; @alphastar].
Complex environmental problems share many similarities to these tasks and games: the need to plan many moves ahead given a large number of possible outcomes, to account for uncertainty and to respond with contingency to the unexpected.
RL agents typically develop strategies by interacting with simulators, a practice that should not be unsettling to ecologists since learning from simulators is common across ecology.
Rich, processes-based simulations such as the SORTIE model in forest management [@sortie], Ecopath with Ecosim in fisheries management [@ecopath], or climate change policy models [@dice] are already used to explore scenarios and inform ecosystem management.
Decision-theoretic approaches based on optimal control techniques can only find the best strategy in the simplest of ecological models; the so called "curse of dimensionality" makes problems with a large number of states or actions intractable by conventional methods [@Possingham2006; @Marescot2013; @ferrer-mestres_k-n-momdps_2021; @chades_primer_2021].
Neural-network-based RL techniques, referred to as *deep RL*, have proven particularly effective in problems involving complex, high-dimensional spaces that have previously proven intractable to classical methods.

@@

Neural networks become useful in RL when the environment has a large observation-action space^[Conventionally, an observation-action space is considered to be large when it is non-tabular, i.e. cannot be represented in a computationally tractable table.], which happens frequently with realistic decision-making problems. 
Whenever there is a need for an agent to approximate some function, typically to model the policy and/or the transition dynamics, neural networks can be used in this capacity due to their property of being general function approximators [@universalapproximators].
Although there are other function approximators that can be used in RL, e.g. Gaussian processes [@grande14], neural networks have excelled in this role because of their ability to learn complex, non-linear, high dimensional functions and their ability to adapt given new information [@briefsurveydrl].
There is a multitude of deep RL algorithms since there are many design choices that can be made in constructing a deep RL agent -- see Appendix A for more detail on these engineering decisions. 
In Table 1, we present some of the more common deep RL algorithms which serve as good reference points for the current state of deep RL.

### 2022-05-27 manuscript/revision_response.Rmd
Some edits, more to come

It is possible to use techniques from supervised learning and unsupervised learning in RL. Two examples that come to mind are behavior cloning and “CURL: Contrastive Unsupervised Representations for Reinforcement Learning” by Srinivas et al. which apply supervised and unsupervised learning techniques respectively. Reinforcement learning is a sprawling discipline and since this is an introductory piece in which we don’t want to overwhelm the reader, we think it is better to focus on more commonly encountered subjects in the field.

It is possible to use neural networks to model the transition dynamics whether that is in the agent or in the simulator. The first case would be an instance of model-based RL, where the agent is modeling the environment; this approach is quite common. We do not mention that neural networks can be used to approximate the transition dynamics explicitly in the manuscript, but implicitly: “Whenever there is a need for an agent to approximate some function, say a policy function, neural networks can be used in this capacity due to their property of being general function approximators.”

@@

We’ve updated this statement, there are a handful applications of deep RL in ecology. !!Need to do this!!

>>>>

It is possible to use techniques from supervised learning and unsupervised learning in RL. Two examples that come to mind are behavior cloning and “CURL: Contrastive Unsupervised Representations for Reinforcement Learning” by Srinivas et al. Reinforcement learning is a sprawling discipline and since this is an introductory piece where we don’t want to overwhelm the reader, we think it is better to focus on more commonly encountered subjects in the field.

This is a good point that we have attempted to clarify in the manuscript:

"Whenever there is a need for an agent to approximate some function, typically to model the policy and/or the transition dynamics, neural networks can be used in this capacity due to their property of being general function approximators."

@@

We’ve updated this statement as we have found a few noteworthy applications in ecology. Cite !!line!!.
